Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Work further in combining DQ papers

\subsection{Data Quality Metrics}

@@

Another important area of data quality is what methodologies can be applied by
organizations in order to improve it. There are several studies that tried to
propose such methodologies. A general overview of such techniques was presented 
by \citet{pipino2002data} - they wanted to present ways of developing usable 
data quality methods that organizations can implement in their own internal 
processes. After reviewing various techniques of assessing data quality in
information systems, they reached the conclusion that there is no universal 
approach to assess data quality as it heavily depends on the context where it is
analysed.

@@

@@

\textbf{Evaluating IT Quality in E-Government 
        Environment}\cite{prybutok2008evaluating}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper is to identify if leadership and IT quality
    can lead to positive outcomes in an e-government environment.
  \item \textbf{What was the method?}
    They conducted a web survey to gather data and test their hypotheses. They
    assessed the City of Denton's e-government initiatives, including current 
    plans and implementations.
  \item \textbf{What did they learn?}
    They learned that the MBNQA leadership triad (leadership, strategic
    planning and customer/market focus) had a positive impact on the IT quality
    triad (information, system and service quality). Moreover, they found out
    that both leadership and IT quality improved the benefits.
  \item \textbf{Relevance to our work}: even though the environment presented
    in the paper was an e-government, it is useful to see how the organization 
    around a project as well as IT quality can lead to a better functioning of the 
    system. Thus, in our research, it can prove helpful in choosing the right 
    open source project to gather and analyse the data from.
\end{itemize}

@@

\textbf{Metrics for Measuring Data Quality}\cite{Heinrich2007MetricsDataQuality}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors of the paper aimed to answer the two main research questions:
      \begin{itemize}
        \item how can data quality be measured as metrics?
        \item what can be done in regards to data quality and what economic
          consequences would it bring?
      \end{itemize}
  \item \textbf{What was the method?}
    They applied the metric for timeliness at a major German mobile services
    provider. Due to some Data Quality issues the company was having, they had
    lower mailing campaign success rates, but after applying the metrics, the 
    company was able to establish a direct connection between the results of
    measuring data quality and the success rates of campaigns.
  \item \textbf{What did they learn?}
    For some practical problems, the metrics that they applied in regards to
    data quality proved to be quite appropriate. As they designed the metrics
    to revolve around interpretability and cardinality, they could quantify
    data quality, thus they could analyse the economical impact.
  \item \textbf{Relevance to our work}: this paper could possibly help us in
    measuring data quality. This is an important step in our research as we 
    specifically need to measure quality in software tickets.
\end{itemize}

>>>>

\subsection{Data Quality and Metrics}

@@

Another important area of data quality is what methodologies or techniques can 
be applied by organizations in order to improve DQ. There are several studies 
that tried to propose such methodologies. A general overview of such techniques 
was presented by \citet{pipino2002data} - they wanted to present ways of 
developing usable  data quality methods that organizations can implement in 
their own internal processes. After reviewing various techniques of assessing 
data quality in information systems, they reached the conclusion that there is 
no universal approach to assess data quality as it heavily depends on the 
context where it is analysed.

@@

However, there are other aspects that can be investigated when trying to measure
data quality. For example, \citet{prybutok2008evaluating} tried to find if 
leadership and information quality can lead to positive outcomes in an 
e-government's data quality. They conducted a web survey to gather data and test 
their hypotheses. Afterwards, they assessed the City of Denton's e-government 
initiatives, including current plans and implementations. They learned that the 
MBNQA leadership triad (leadership, strategic planning and customer/market focus) 
had a positive impact on the IT quality triad (information, system and service 
quality). Moreover, they found out that both leadership and IT quality improved 
the benefits.

@@

@@
